Analysis

### 2017-03-28 Analysis.Rmd
Minor edits to text in Analysis and main README
Add analysis for tiller sheath blight incidence and corresponding graphs

#### Random effects
Fitting the models with the default iterations resulted in some less than
acceptable models. Because of this, the number of iterations has been increased,
`nitt = 5e+05` and `burnin = 5000` and `thin = 100`. This results in much
smaller errors for random effects and better models.

@@

# diagnostic line plots for replicate
plot_diagnostic_lines(d = reps,
                      x = x,
                      title = "2015 Diagnostic Plots for Leaf ShB Reps")

# posterior distributions for replicate
plot_replicate_posteriors(d = reps,
                          title = "2015 Replicate Posteriors for Leaf ShB Reps")

# diagnostic line plots for treatments
plot_diagnostic_lines(d = trts,
                      x = x,
                      title = "2015 Diagnostic Plots for Leaf ShB Treatments")

# Posterior distributions for treatment
plot_treatment_posteriors(d = trts,
                          title = "2015 Treatment Posteriors for Leaf ShB Treatments")

@@

# plot joint distibution of error
rdf <- data.frame(LShB_lmm_2015$VCV)
plot_joint_random_error_dist(d = rdf,
                             title = ("2015 Leaf ShB Random Error Distribution"))
```

@@

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_lmm_2015 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE, ~REP, 
                          data = as.data.frame(AUDPS_2015),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

summary(TShB_lmm_2015)

# create data frames for generating diagnostic plots
reps <- data.frame(TShB_lmm_2015$Sol[, c(1, 7:10)])
reps <- melt(reps)

trts <-  data.frame(TShB_lmm_2015$Sol[, 2:6])
names(trts)[names(trts) == "WMGTFLD.NRTE100"] <- "FLD.NRTE100"
names(trts)[names(trts) == "WMGTFLD.NRTE120"] <- "FLD.NRTE120"
trts <- melt(trts)

# Create a dummy x-axis variable for plotting
x <- 1:nrow(TShB_lmm_2015$Sol)

# diagnostic line plots for replicate
plot_diagnostic_lines(d = reps,
                      x = x,
                      title = "2015 Diagnostic Plots for Leaf ShB Reps")

# posterior distributions for replicate
plot_replicate_posteriors(d = reps,
                          title = "2015 Replicate Posteriors for Leaf ShB Reps")

# diagnostic line plots for treatments
plot_diagnostic_lines(d = trts,
                      x = x,
                      title = "2015 Diagnostic Plots for Leaf ShB Treatments")

# Posterior distributions for treatment
plot_treatment_posteriors(d = trts,
                          title = "2015 Treatment Posteriors for Leaf ShB Treatments")

# check random effects
plotTrace(TShB_lmm_2015$VCV, log = TRUE)

# plot joint distibution of error
rdf <- data.frame(TShB_lmm_2015$VCV)
plot_joint_random_error_dist(d = rdf,
                             title = ("2015 Leaf ShB Random Error Distribution"))
```

@@

# diagnostic line plots for replicate
plot_diagnostic_lines(d = reps,
                      x = x,
                      title = "2016 Diagnostic Plots for Leaf ShB Reps")

# posterior distributions for replicate
plot_replicate_posteriors(d = reps,
                          title = "2016 Replicate Posteriors for Leaf ShB Reps")

# diagnostic line plots for treatments
plot_diagnostic_lines(d = trts,
                      x = x,
                      title = "2016 Diagnostic Plots for Leaf ShB Treatments")

# Posterior distributions for treatment
plot_treatment_posteriors(d = trts,
                          title = "2016 Treatment Posteriors for Leaf ShB Treatments")

@@

# plot joint distibution of error
rdf <- data.frame(LShB_lmm_2015$VCV)
plot_joint_random_error_dist(d = rdf,
                             title = ("2016 Leaf ShB Random Error Distribution"))
```

@@

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_lmm_2016 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE, ~REP, 
                          data = as.data.frame(AUDPS_2016),
                          verbose = FALSE,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          prior = eprior,
                          pr = TRUE)

summary(TShB_lmm_2016)

# create data frames for generating diagnostic plots
reps <- data.frame(TShB_lmm_2016$Sol[, c(1, 5:8)])
reps <- melt(reps)

trts <-  data.frame(TShB_lmm_2016$Sol[, 2:4])
names(trts)[names(trts) == "WMGTFLD.NRTE180"] <- "FLD.NRTE180"
trts <- melt(trts)

# Create a dummy x-axis variable for plotting
x <- 1:nrow(TShB_lmm_2016$Sol)

# diagnostic line plots for replicate
plot_diagnostic_lines(d = reps,
                      x = x,
                      title = "2016 Diagnostic Plots for Leaf ShB Reps")

# posterior distributions for replicate
plot_replicate_posteriors(d = reps,
                          title = "2016 Replicate Posteriors for Leaf ShB Reps")

# diagnostic line plots for treatments
plot_diagnostic_lines(d = trts,
                      x = x,
                      title = "2106 Diagnostic Plots for Leaf ShB Treatments")

# Posterior distributions for treatment
plot_treatment_posteriors(d = trts,
                          title = "2016 Treatment Posteriors for Leaf ShB Treatments")

# check random effects
plotTrace(TShB_lmm_2016$VCV, log = TRUE)

# plot joint distibution of error
rdf <- data.frame(TShB_lmm_2016$VCV)
plot_joint_random_error_dist(d = rdf,
                             title = ("2016 Leaf ShB Random Error Distribution"))
```

>>>>

#### Iterations
Fitting the models with the default iterations resulted in some less than
acceptable models. Because of this, the number of iterations has been increased,
`nitt = 5e+05` and `burnin = 5000` and `thin = 100`. This results in much
smaller errors for random effects and better models.

@@

# Create a dummy x-axis variable for plotting
x <- 1:nrow(LShB_lmm_2015$Sol)

# diagnostic line plots for replicate
plot_diagnostic_lines(d = reps,
                      x = x,
                      title = "2015 Diagnostic Plots for Replicates, Leaf ShB Severity")

# posterior distributions for replicate
plot_replicate_posteriors(d = reps,
                          title = "2015 Reps Replicate Posteriors for Replicates, Leaf ShB Severity")

# diagnostic line plots for treatments
plot_diagnostic_lines(d = trts,
                      x = x,
                      title = "2015 Diagnostic Plots for Treatments, Leaf ShB Severity")

# Posterior distributions for treatment
plot_treatment_posteriors(d = trts,
                          title = "2015 Posteriors for Treatments, Leaf ShB Severity")

@@

# plot joint distibution of error
rdf <- data.frame(LShB_lmm_2015$VCV)
plot_joint_random_error_dist(d = rdf,
                             title = ("2015 Random Error Distribution for Leaf ShB Severity"))
```

@@

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_severity_lmm_2015 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE, ~REP, 
                          data = as.data.frame(AUDPS_2015),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

summary(TShB_severity_lmm_2015)

# create data frames for generating diagnostic plots
reps <- data.frame(TShB_severity_lmm_2015$Sol[, c(1, 7:10)])
reps <- melt(reps)

trts <-  data.frame(TShB_severity_lmm_2015$Sol[, 2:6])
names(trts)[names(trts) == "WMGTFLD.NRTE100"] <- "FLD.NRTE100"
names(trts)[names(trts) == "WMGTFLD.NRTE120"] <- "FLD.NRTE120"
trts <- melt(trts)

# Create a dummy x-axis variable for plotting
x <- 1:nrow(TShB_severity_lmm_2015$Sol)

# diagnostic line plots for replicate
plot_diagnostic_lines(d = reps,
                      x = x,
                      title = "2015 Diagnostic Plots for Replicates, Tiller ShB Severity")

# posterior distributions for replicate
plot_replicate_posteriors(d = reps,
                          title = "2015 Reps Replicate Posteriors for Replicates, Tiller ShB Severity")

# diagnostic line plots for treatments
plot_diagnostic_lines(d = trts,
                      x = x,
                      title = "2015 Diagnostic Plots for Treatments, Tiller ShB Severity")

# Posterior distributions for treatment
plot_treatment_posteriors(d = trts,
                          title = "2015 Posteriors for Treatments, Tiller ShB Severity")

# check random effects
plotTrace(TShB_severity_lmm_2015$VCV, log = TRUE)

# plot joint distibution of error
rdf <- data.frame(TShB_severity_lmm_2015$VCV)
plot_joint_random_error_dist(d = rdf,
                             title = ("2015 Random Error Distribution for Tiller ShB Severity"))
```

### 2015 Tiller Sheath Blight Incidence Model
```{r}

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_incidence_lmm_2015 <- MCMCglmm(TShB_incidence_mean ~ WMGT * NRTE, ~REP, 
                          data = as.data.frame(AUDPS_2015),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

summary(TShB_incidence_lmm_2015)

# create data frames for generating diagnostic plots
reps <- data.frame(TShB_incidence_lmm_2015$Sol[, c(1, 7:10)])
reps <- melt(reps)

trts <-  data.frame(TShB_incidence_lmm_2015$Sol[, 2:6])
names(trts)[names(trts) == "WMGTFLD.NRTE100"] <- "FLD.NRTE100"
names(trts)[names(trts) == "WMGTFLD.NRTE120"] <- "FLD.NRTE120"
trts <- melt(trts)

# Create a dummy x-axis variable for plotting
x <- 1:nrow(TShB_incidence_lmm_2015$Sol)

# diagnostic line plots for replicate
plot_diagnostic_lines(d = reps,
                      x = x,
                      title = "2015 Diagnostic Plots for Replicates, Tiller ShB Incidence")

# posterior distributions for replicate
plot_replicate_posteriors(d = reps,
                          title = "2015 Reps Replicate Posteriors for Replicates, Tiller ShB Incidence")

# diagnostic line plots for treatments
plot_diagnostic_lines(d = trts,
                      x = x,
                      title = "2015 Diagnostic Plots for Treatments, Tiller ShB Incidence")

# Posterior distributions for treatment
plot_treatment_posteriors(d = trts,
                          title = "2015 Posteriors for Treatments, Tiller ShB Incidence")

# check random effects
plotTrace(TShB_incidence_lmm_2015$VCV, log = TRUE)

# plot joint distibution of error
rdf <- data.frame(TShB_incidence_lmm_2015$VCV)
plot_joint_random_error_dist(d = rdf,
                             title = ("2015 Random Error Distribution for Tiller ShB Incidence"))
```

@@

# diagnostic line plots for replicate
plot_diagnostic_lines(d = reps,
                      x = x,
                      title = "2016 Diagnostic Plots for Replicates, Leaf ShB Severity")

# posterior distributions for replicate
plot_replicate_posteriors(d = reps,
                          title = "2016 Reps Replicate Posteriors for Replicates, Leaf ShB Severity")

# diagnostic line plots for treatments
plot_diagnostic_lines(d = trts,
                      x = x,
                      title = "2016 Diagnostic Plots for Treatments, Leaf ShB Severity")

# Posterior distributions for treatment
plot_treatment_posteriors(d = trts,
                          title = "2016 Posteriors for Treatments, Leaf ShB Severity")

@@

# plot joint distibution of error
rdf <- data.frame(LShB_lmm_2016$VCV)
plot_joint_random_error_dist(d = rdf,
                             title = ("2016 Random Error Distribution for Leaf ShB Severity"))
```

@@

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_severity_lmm_2016 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE, ~REP, 
                          data = as.data.frame(AUDPS_2016),
                          verbose = FALSE,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          prior = eprior,
                          pr = TRUE)

summary(TShB_severity_lmm_2016)

# create data frames for generating diagnostic plots
reps <- data.frame(TShB_severity_lmm_2016$Sol[, c(1, 5:8)])
reps <- melt(reps)

trts <-  data.frame(TShB_severity_lmm_2016$Sol[, 2:4])
names(trts)[names(trts) == "WMGTFLD.NRTE180"] <- "FLD.NRTE180"
trts <- melt(trts)

# Create a dummy x-axis variable for plotting
x <- 1:nrow(TShB_severity_lmm_2016$Sol)
# diagnostic line plots for replicate
plot_diagnostic_lines(d = reps,
                      x = x,
                      title = "2016 Diagnostic Plots for Replicates, Tiller ShB Severity")

# posterior distributions for replicate
plot_replicate_posteriors(d = reps,
                          title = "2016 Reps Replicate Posteriors for Replicates, Tiller ShB Severity")

# diagnostic line plots for treatments
plot_diagnostic_lines(d = trts,
                      x = x,
                      title = "2016 Diagnostic Plots for Treatments, Tiller ShB Severity")

# Posterior distributions for treatment
plot_treatment_posteriors(d = trts,
                          title = "2016 Posteriors for Treatments, Tiller ShB Severity")

# check random effects
plotTrace(TShB_severity_lmm_2016$VCV, log = TRUE)

# plot joint distibution of error
rdf <- data.frame(TShB_severity_lmm_2016$VCV)
plot_joint_random_error_dist(d = rdf,
                             title = ("2016 Random Error Distribution for Tiller ShB Severity"))
```

### 2016 Tiller Sheath Blight Incidence Model
```{r}

eprior <- list(R = list(V = 1, nu = 0.02),
               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
TShB_incidence_lmm_2016 <- MCMCglmm(TShB_incidence_mean ~ WMGT * NRTE, ~REP, 
                          data = as.data.frame(AUDPS_2016),
                          verbose = FALSE,
                          prior = eprior,
                          nitt = 5e+05,
                          burnin = 5000,
                          thin = 100,
                          pr = TRUE)

summary(TShB_incidence_lmm_2016)

# create data frames for generating diagnostic plots
reps <- data.frame(TShB_incidence_lmm_2016$Sol[, c(1, 5:8)])
reps <- melt(reps)

trts <-  data.frame(TShB_incidence_lmm_2016$Sol[, 2:4])
names(trts)[names(trts) == "WMGTFLD.NRTE100"] <- "FLD.NRTE100"
names(trts)[names(trts) == "WMGTFLD.NRTE120"] <- "FLD.NRTE120"
trts <- melt(trts)

# Create a dummy x-axis variable for plotting
x <- 1:nrow(TShB_incidence_lmm_2016$Sol)

# diagnostic line plots for replicate
plot_diagnostic_lines(d = reps,
                      x = x,
                      title = "2016 Diagnostic Plots for Replicates, Tiller ShB Incidence")

# posterior distributions for replicate
plot_replicate_posteriors(d = reps,
                          title = "2016 Reps Replicate Posteriors for Replicates, Tiller ShB Incidence")

# diagnostic line plots for treatments
plot_diagnostic_lines(d = trts,
                      x = x,
                      title = "2016 Diagnostic Plots for Treatments, Tiller ShB Incidence")

# Posterior distributions for treatment
plot_treatment_posteriors(d = trts,
                          title = "2016 Posteriors for Treatments, Tiller ShB Incidence")

# check random effects
plotTrace(TShB_incidence_lmm_2016$VCV, log = TRUE)

# plot joint distibution of error
rdf <- data.frame(TShB_incidence_lmm_2016$VCV)
plot_joint_random_error_dist(d = rdf,
                             title = ("2016 Random Error Distribution for Tiller ShB Incidence"))
```
